---
title: "Lab report knapsack"
author: "Duc Duong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab report knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)

```



## Opening speech
This is the report for R lab 6. In this repot, I will represent 2 parts:
1. Present the speed of different algorithms
2. Answer questions of the lab.

Before going to the details, let's take a look on how to install the package:
```{r}
devtools::install_github('DucDuong/Lab6R', build_vignettes = TRUE)
```

# 1. The speed of different algorithms

Among there algorithm, brute_force allways the slowest one. Dynamic_knapsack is faster (because of the improve in the algorithm). greedy_knapsack is the fastest one, but it cost is sometime return value is not the optimum one.


# 2. Questions of the lab

Question 1.1.2: How much time does it takes to run the algorithm for n = 16 objects?
For brute_force algorithm, it take the time as follow:

```{r}
library(Lab6R)
data("knapsack_objects")
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
```

Question 1.1.8: What performance gain could you get by parallelizing brute force search?

```{r}
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE)
```

Compare the time when have parallel, we see that the user time is improved.

Question 1.1.3: How much time does it takes to run the algorithm for n = 500 objects?
For dynamic_knapsack algorithm, it take the time as follow:
```{r}
dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500)
```

Question 1.1.4: How much time does it takes to run the algorithm for n = 1000000 objects?

For dynamic_knapsack algorithm, it take the time as follow:

```{r}
set.seed(42)
n <- 1000000
knapsack_objects <-data.frame(
  w=sample(1:10000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
)

greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500)
```

Question 1.1.6: What performance gain could you get by trying to improving your code?

```{r}
library(microbenchmark)
microbenchmark(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
```

